Global Deaths Due to Air Pollution

### 2022-05-01 outline.Rmd
so i didnt change the country name for one year and it printed duplicates. its fixed now

Import the deaths-due-to-air-pollution data
```{r, echo=FALSE}
deaths_df <- data.frame(read.csv("death-rates-from-air-pollution.csv"))
```

We are going to rename a few of the columns and glimpse the data
```{r, echo=FALSE}
colnames(deaths_df) <- c("country", "acronym", "year", "total_deaths", "indoor_deaths", "outdoor_deaths", "ozone_deaths")

@@

Now, let's take a look at the population data.
```{r, echo=FALSE}
world_pop <- read.csv("population_total_long.csv")
glimpse(world_pop)
```

>>>>

Import the deaths-due-to-air-pollution data
```{r}
deaths_df <- data.frame(read.csv("death-rates-from-air-pollution.csv"))
```

We are going to rename a few of the columns and glimpse the data
```{r}
colnames(deaths_df) <- c("country", "acronym", "year", "total_deaths", "indoor_deaths", "outdoor_deaths", "ozone_deaths")

@@

Now, let's take a look at the population data.
```{r}
world_pop <- read.csv("population_total_long.csv")
glimpse(world_pop)
```
